A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-05-07 paper/paper.tex
fix

The idea for such indexed presentation of presheaves over a direct category was introduced at the Univalent Foundations year in the context of defining semi-simplicial types~\cite{}. A couple of constructions were proposed since then. One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over injective monotone maps between finite ordinals. Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}. Another one by Part and Luo, and formalized in the Plastic proof assistant, works generically for any Reedy category with only upwards maps~\cite{part15}.

>>>>

The idea for such indexed presentation of presheaves over a direct category was introduced at the Univalent Foundations year in the context of defining semi-simplicial types~\cite{}. A couple of constructions were proposed since then. One, by Voevodsky~\cite{Voevodsky12}, relies on the presentation of semi-simplicial sets as a presheaf over increasing injective maps between finite ordinals. Another, by the first author, and fully formalized in Coq, relies on the presentation of semi-simplicial sets as a presheaf over face maps~\cite{herbelin15}. Another one by Part and Luo, and formalized in the Plastic proof assistant, works generically for any Reedy category with only upwards maps~\cite{part15}.
